---
title: "ShinyMolBio"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Central Dogma of Molecular Biology}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ShinyMolBio)
```

```{r eval=FALSE}
Author@R:
  c(person(given = "Oriade", 
            family = "Simpson",
            email = "s172084@dtu.dk", 
            role = c("cre", "aut"),
         person(given = "MOLS",
                family = "MOLS",
                role = "aut",
                email = "orie.simpson@gmail.com"))
```

<!-- badges: start -->
<!-- badges: end -->

## Overview

ShinyMolBio is a package regarding the Central Dogma of Molecular Biology.

***

## Installation

The easiest way to get `ShinyMolBio` is to install the whole package:

You can install the development version of `ShinyMolBio` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rforbiodatascience22/group_20_shiny")
```

***

## Usage 

```{r example}
library(ShinyMolBio)
```

***

## Getting help

If you encounter a clear bug, please file an issue with a minimal reproducible example on GitHub.
For questions and other discussion, please email `s172084@dtu.dk` or `orie.simpson@gmail.com`

Please note that this project is released with a Contributor Code of Conduct. By participating in this project you agree to abide by its terms.

